---
title: "Reproducible Research Final Project"
author: "Erim Celen, Ozgur Polat, Bugra Duman"
date: "5/7/2021"
output: 
  html_document:
    theme: united
    highlight: tango
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include=FALSE}
library(readr)
library(tidyverse)
library(plyr)
library(dplyr)
library(kableExtra)
library(caret)
library(nnet)
library(gridExtra)
library(grid)
```

```{r message=FALSE, warning=FALSE, include=FALSE}
data <- read_csv(url("https://www.football-data.co.uk/mmz4281/1920/E0.csv"))
data <- data[1:41]
```


## Data Description

data description here

## Data Analysis

## Teams in the league
```{r fig.align="center", echo=FALSE, message=TRUE, warning=FALSE}
Teams <- 
  data %>%
  select(HomeTeam) %>%
  unique() %>%
  arrange(HomeTeam) %>% 
  setNames(c("value"))


kable(col.names = NULL,list(Teams[1:10,],Teams[11:nrow(Teams),])) %>%
kable_styling(position = "center")

```


## Standings Table

```{r include=FALSE}
points_table <-
  data %>%
  summarize(HomeTeam,AwayTeam,FTR) %>%
  mutate(class1 = ifelse(FTR == "D",1,3)) %>%
  pivot_longer(cols = c("HomeTeam","AwayTeam"))

points_table$class2 <- ifelse(substr(points_table$name, 1,1) == substr(points_table$FTR, 1,1),3,0)

points_table <- 
  points_table %>%
  filter(class1 == 1 | class2 == 3) %>%
  mutate(final = ifelse(class1 != class2, class1, class2)) %>% 
  group_by(value) %>%
  summarise_at(vars(final),
               list(P=sum))

wins_table <- 
  data %>%
  summarize(HomeTeam,AwayTeam,FTR) %>%
  filter(FTR != "D") %>%
  pivot_longer(cols = c("HomeTeam","AwayTeam"))

wins_table$w <- substr(wins_table$name, 1,1) == substr(wins_table$FTR, 1,1)  

wins_table <- 
  wins_table %>%
  filter(w == TRUE) %>%
  group_by(value) %>%
  summarise_at(vars(w),
               list(W=sum))

lost_table <-
  data %>%
  summarize(HomeTeam,AwayTeam,FTR) %>%
  filter(FTR != "D") %>%
  pivot_longer(cols = c("HomeTeam","AwayTeam"))

lost_table$l <- substr(lost_table$name, 1,1) != substr(lost_table$FTR, 1,1)

lost_table <- 
  lost_table %>%
  filter(l == TRUE) %>%
  group_by(value) %>%
  summarise_at(vars(l),
               list(L=sum))

draw_table <- 
  data %>%
  summarize(HomeTeam,AwayTeam,FTR) %>%
  filter(FTR == "D") %>%
  pivot_longer(cols = c("HomeTeam","AwayTeam")) %>%
  mutate(d = ifelse(FTR == "D",1,0)) %>% 
  group_by(value) %>% 
  summarise_at(vars(d),
               list(D=sum))

gfh_table <-
  data %>% 
  group_by(HomeTeam) %>%
  summarise_at(vars(FTHG),
               list(GFH=sum)) %>% 
  setNames(c("value","GFH"))

gfa_table <-
  data %>% 
  group_by(AwayTeam) %>%
  summarise_at(vars(FTAG),
               list(GFA=sum)) %>% 
  setNames(c("value","GFA"))

gf_table <- 
  ddply(merge(gfa_table, gfh_table, by = "value"),.(value),summarise, GF=sum(GFH+GFA))

gah_table <-
  data %>% 
  group_by(HomeTeam) %>%
  summarise_at(vars(FTAG),
               list(GAH=sum)) %>% 
  setNames(c("value","GAH"))

gaa_table <-
  data %>% 
  group_by(AwayTeam) %>%
  summarise_at(vars(FTHG),
               list(GAA=sum)) %>% 
  setNames(c("value","GAA"))

ga_table <- 
  ddply(merge(gah_table, gaa_table, by = "value"),.(value),summarise, GA=sum(GAH+GAA))


gd_table <-
  ddply(merge(ga_table, gf_table, by = "value"),.(value),summarise, GD=sum(GF-GA))

```


```{r echo=FALSE}
standings <- cbind(Teams,wins_table,draw_table,lost_table,gf_table,ga_table,gd_table,points_table)
standings <- standings[,c(-2,-4,-6,-8,-10,-12,-14)]
colnames(standings)[1] <- "Teams"
standings %>% 
  kable("html",row.names = FALSE) %>%
  kable_styling(font_size = 20,bootstrap_options = c("striped","hover")) 
```


## Number of Wins {.tabset}

### Table

```{r echo=FALSE}
winners <- 
  data %>%
  summarize(HomeTeam,AwayTeam,FTR) %>%
  filter(FTR != "D") %>%
  pivot_longer(cols = c("HomeTeam","AwayTeam"))

winners$w <- substr(winners$name, 1,1) == substr(winners$FTR, 1,1)  
  
winners %>%
  filter(w == TRUE) %>%
  group_by(value) %>%
  summarise_at(vars(w),
               list(W=sum)) %>% 
  arrange(desc(W)) %>%
  head(5) %>%
  kable(col.names = c("Teams","Number of Wins"),digits = 2,"html",row.names = FALSE) %>%
  kable_styling(font_size = 20,bootstrap_options = c("striped","hover")) 
  
```

### Code

```{r}
winners <- 
  data %>%
  summarize(HomeTeam,AwayTeam,FTR) %>%
  filter(FTR != "D") %>%
  pivot_longer(cols = c("HomeTeam","AwayTeam"))

winners$w <- substr(winners$name, 1,1) == substr(winners$FTR, 1,1)  
  
winners %>%
  filter(w == TRUE) %>%
  group_by(value) %>%
  summarise_at(vars(w),
               list(W=sum)) %>% 
  arrange(desc(W)) %>%
  kable(col.names = c("Teams","Number of Wins"),digits = 2,"html",row.names = FALSE) %>%
  kable_styling(font_size = 20,bootstrap_options = c("striped","hover")) 
  
```

## Percentage of Shots on Target

```{r include=FALSE}
table <- 
  data %>% 
  summarise('Home Shot' = sum(HS), 
            'Home Shot on Target' = sum(HST), 
            'Away Shot' = sum(AS), 
            'Away Shot on Target' = sum(AST)) %>% 
  pivot_longer(everything())

table <- 
  table %>% 
  mutate(place = substr(name,1,4))

p1 <-  ggplot(table, aes(x=name, y=value, fill=place)) + 
            geom_bar(stat = "identity") +
            geom_text(aes(label = value)) +
            theme(axis.title.x = element_blank(),
                  axis.title.y = element_blank(),
                  axis.text.y = element_blank(),
                  axis.text.x = element_text(angle = 45,size = 8,hjust = 1),
                  axis.ticks.y = element_blank(),
                  legend.title = element_blank()) +
            scale_fill_manual(values = c("#d8b365", "#5ab4ac"))


proportions <- as.data.frame(c("Home","Away")) %>% setNames(c("name"))
proportions$value <- c(round(table[2,2] / table[1, 2],4) * 100,round(table[4,2] / table[3,2],4) * 100)
proportions$value = paste0('%', proportions$value)
```

```{r fig.align="center", echo=FALSE}
t1 <- tableGrob(proportions, theme = ttheme_minimal(), rows = NULL,cols = NULL)

grid.arrange(p1,t1, nrow=1)

```


## Most Played Game Hours {.tabset}

### Table

```{r echo=FALSE, message=FALSE, warning=FALSE}
data %>%
  group_by(Time) %>%
  tally(sort = T) %>%
  top_n(3) %>%
  kable(col.names = c("Time","Game Played"),digits = 2,"html",row.names = FALSE) %>%
  kable_styling(font_size = 20,bootstrap_options = c("striped","hover"))  
```

### Code

```{r message=FALSE, warning=FALSE}
data %>%
  group_by(Time) %>%
  tally(sort = T) %>%
  top_n(3) %>%
  kable(col.names = c("Time","Game Played"),digits = 2,"html",row.names = FALSE) %>%
  kable_styling(font_size = 20,bootstrap_options = c("striped","hover")) 
```


## Full Time Results {.tabset}

Home team always has the advantage since they have more fans in the stadium.

### Table

```{r echo=FALSE, message=FALSE, warning=FALSE}
data %>% 
  mutate(FTR = as_factor(FTR)) %>%
  mutate(FTR = recode_factor(FTR,A = "Away", H = "Home", D = "Draw")) %>%
  select(FTR) %>% 
  count() %>% 
  arrange(desc(freq)) %>%
  kable(col.names = c("Team","Wins"),"html",row.names = FALSE) %>%
  kable_styling(font_size = 20,bootstrap_options = c("striped","hover"))
```

### Table Code

```{r message=FALSE, warning=FALSE}
data %>% 
  mutate(FTR = as_factor(FTR)) %>%
  mutate(FTR = recode_factor(FTR,A = "Away", H = "Home", D = "Draw")) %>%
  select(FTR) %>% 
  count() %>% 
  arrange(desc(freq)) %>%
  kable(col.names = c("Team","Wins"),"html",row.names = FALSE) %>%
  kable_styling(font_size = 20,bootstrap_options = c("striped","hover"))
```

### Plot

```{r echo=FALSE, message=FALSE, warning=FALSE}
data %>% 
  mutate(FTR = as_factor(FTR)) %>%
  mutate(FTR = recode_factor(FTR,A = "Away", H = "Home", D = "Draw")) %>%
  select(FTR) %>%
  count() %>%
  ggplot(aes(x="", y=freq, fill=FTR)) +
  geom_bar(stat = "identity", width=1) +
  coord_polar(theta = "y", start = 0) +
  scale_fill_manual(values=c("#B81D13", "#008450","#EFB700")) +
  geom_text(aes(label = freq),position = position_stack(vjust = 0.5)) +
  theme_void() +
  labs(fill = NULL)

```

### Plot Code

```{r message=FALSE, warning=FALSE}
data %>% 
  mutate(FTR = as_factor(FTR)) %>%
  mutate(FTR = recode_factor(FTR,A = "Away", H = "Home", D = "Draw")) %>%
  select(FTR) %>%
  count() %>%
  ggplot(aes(x="", y=freq, fill=FTR)) +
  geom_bar(stat = "identity", width=1) +
  coord_polar(theta = "y", start = 0) +
  scale_fill_manual(values=c("#B81D13", "#008450","#EFB700")) +
  geom_text(aes(label = freq),position = position_stack(vjust = 0.5)) +
  theme_void() +
  labs(fill = NULL)

```

## Games with most goals {.tabset}

### Table

```{r echo=FALSE, message=FALSE, warning=FALSE}
data %>%
  select(Date,HomeTeam,AwayTeam,FTHG,FTAG) %>%
  rowwise() %>%
  mutate(m = sum(c(FTHG,FTAG))) %>%
  ungroup() %>%
  arrange(desc(m)) %>%
  head(3) %>%
  select(-m)%>%
  kable(digits = 2,"html",row.names = FALSE) %>%
  kable_styling(font_size = 20,bootstrap_options = c("striped","hover"))
```

### Code

```{r message=FALSE, warning=FALSE}
data %>%
  select(Date,HomeTeam,AwayTeam,FTHG,FTAG) %>%
  rowwise() %>%
  mutate(m = sum(c(FTHG,FTAG))) %>%
  ungroup() %>%
  arrange(desc(m)) %>%
  head(3) %>%
  select(-m)%>%
  kable(digits = 2,"html",row.names = FALSE) %>%
  kable_styling(font_size = 20,bootstrap_options = c("striped","hover"))
```

## Average Odds {.tabset}

### Table

```{r echo=FALSE, message=FALSE, warning=FALSE}
data %>%
  mutate(B365s = rowSums(.[grep("B365",names(.))]),
         BWs = rowSums(.[grep("BW",names(.))]),
         IWs = rowSums(.[grep("IW",names(.))]),
         PSs = rowSums(.[grep("PS",names(.))]),
         WHs = rowSums(.[grep("WH",names(.))]),
         VCs = rowSums(.[grep("VC",names(.))])) %>%
  summarise(Bet365 = mean(B365s),
            BetWin = mean(BWs),
            Interwetten = mean(IWs),
            Pinnacle = mean(PSs),
            WilliamHill = mean(WHs),
            VCBet = mean(VCs))%>%
  pivot_longer(everything()) %>%
  arrange(desc(value)) %>%
  kable(digits = 2,"html",row.names = FALSE, col.names = c("Bet Platform","Average of Total odds")) %>%
  kable_styling(font_size = 20,bootstrap_options = c("striped","hover"))
  
```

### Code

```{r message=FALSE, warning=FALSE}
data %>%
  mutate(B365s = rowSums(.[grep("B365",names(.))]),
         BWs = rowSums(.[grep("BW",names(.))]),
         IWs = rowSums(.[grep("IW",names(.))]),
         PSs = rowSums(.[grep("PS",names(.))]),
         WHs = rowSums(.[grep("WH",names(.))]),
         VCs = rowSums(.[grep("VC",names(.))])) %>%
  summarise(Bet365 = mean(B365s),
            BetWin = mean(BWs),
            Interwetten = mean(IWs),
            Pinnacle = mean(PSs),
            WilliamHill = mean(WHs),
            VCBet = mean(VCs))%>%
  pivot_longer(everything()) %>%
  arrange(desc(value)) %>%
  kable(digits = 2,"html",row.names = FALSE, col.names = c("Bet Platform","Average of Total odds")) %>%
  kable_styling(font_size = 20,bootstrap_options = c("striped","hover"))
  
```

## Mean of Cards {.tabset}

### Table

```{r echo=FALSE, message=FALSE, warning=FALSE}
data %>%
  mutate(YellowCards = rowSums(select_(.,"HY","AY")),
         RedCards = rowSums(select_(.,"HR","AR"))) %>%
  summarise(RedCard = mean(RedCards) ,
            YellowCard = mean(YellowCards )) %>%
  pivot_longer(everything()) %>%
  kable(digits = 2,"html", row.names = FALSE, col.names = c("Type of Card","Average of Card per game")) %>%
  kable_styling(font_size = 20,bootstrap_options = c("striped","hover")) %>%
  row_spec(1,background = "#FF0000",color = "black") %>%
  row_spec(2,background = "yellow",color = "black")
```

### Code

```{r message=FALSE, warning=FALSE}
data %>%
  mutate(YellowCards = rowSums(select_(.,"HY","AY")),
         RedCards = rowSums(select_(.,"HR","AR"))) %>%
  summarise(RedCard = mean(RedCards) ,
            YellowCard = mean(YellowCards )) %>%
  pivot_longer(everything()) %>%
  kable(digits = 2,"html", row.names = FALSE, col.names = c("Type of Card","Average of Card per game")) %>%
  kable_styling(font_size = 20,bootstrap_options = c("striped","hover")) %>%
  row_spec(1,background = "#FF0000",color = "black") %>%
  row_spec(2,background = "yellow",color = "black")
```

## En cok sut ceken 5 takim {.tabset}

### Table

```{r echo=FALSE, message=FALSE, warning=FALSE}
HomeShot <- data %>%
                group_by(HomeTeam) %>%
                summarise(HomeTeam,HS) %>%
                pivot_longer(cols = HS) %>% 
                group_by(HomeTeam) %>% 
                summarise_at(vars(value),list(HomeShots=sum)) %>% 
                setNames(c("Team","HomeShots"))
                

AwayShot <- data %>%
                group_by(AwayTeam) %>%
                summarise(AwayTeam,AS) %>%
                pivot_longer(cols = AS) %>%
                group_by(AwayTeam) %>% 
                summarise_at(vars(value),list(AwayShots = sum)) %>% 
                setNames(c("Team","AwayShots"))

TotalShot <- merge(HomeShot,AwayShot, by = "Team")

TotalShot %>%
  mutate(TotalShots = rowSums(select_(.,"HomeShots","AwayShots"))) %>%
  arrange(desc(TotalShots)) %>%
  head(5) %>%
  kable(digits = 2,"html",row.names = FALSE) %>%
  kable_styling(font_size = 20,bootstrap_options = c("striped","hover"))
```

### Code

```{r message=FALSE, warning=FALSE}
HomeShot <- data %>%
                group_by(HomeTeam) %>%
                summarise(HomeTeam,HS) %>%
                pivot_longer(cols = HS) %>% 
                group_by(HomeTeam) %>% 
                summarise_at(vars(value),list(HomeShots=sum)) %>% 
                setNames(c("Team","HomeShots"))
                

AwayShot <- data %>%
                group_by(AwayTeam) %>%
                summarise(AwayTeam,AS) %>%
                pivot_longer(cols = AS) %>%
                group_by(AwayTeam) %>% 
                summarise_at(vars(value),list(AwayShots = sum)) %>% 
                setNames(c("Team","AwayShots"))

TotalShot <- merge(HomeShot,AwayShot, by = "Team")

TotalShot %>%
  mutate(TotalShots = rowSums(select_(.,"HomeShots","AwayShots"))) %>%
  arrange(desc(TotalShots)) %>%
  head(5) %>%
  kable(digits = 2,"html",row.names = FALSE) %>%
  kable_styling(font_size = 20,bootstrap_options = c("striped","hover"))
```

## En cok foul yapan 5 takim {.tabset}

### Table

```{r echo=FALSE, message=FALSE, warning=FALSE}
HomeOff <- data %>%
                group_by(HomeTeam) %>%
                summarise(HomeTeam,HF) %>%
                pivot_longer(cols = HF) %>%
                group_by(HomeTeam) %>% 
                summarise_at(vars(value),list(HomeOffs = sum))%>% 
                setNames(c("Team","HomeFouls"))


AwayOff <- data %>%
                group_by(AwayTeam) %>%
                summarise(AwayTeam,AF) %>%
                pivot_longer(cols = AF) %>%
                group_by(AwayTeam) %>% 
                summarise_at(vars(value),list(AwayOffs = sum)) %>% 
                setNames(c("Team","AwayFouls"))

TotalOff <- merge(HomeOff,AwayOff, by = "Team")

TotalOff %>%
  mutate(TotalOffs = rowSums(select_(.,"HomeFouls","AwayFouls"))) %>%
  arrange(desc(TotalOffs)) %>%
  head(5) %>%
  kable(digits = 2,"html",row.names = FALSE) %>%
  kable_styling(font_size = 20,bootstrap_options = c("striped","hover"))
```

### Code

```{r message=FALSE, warning=FALSE}
HomeOff <- data %>%
                group_by(HomeTeam) %>%
                summarise(HomeTeam,HF) %>%
                pivot_longer(cols = HF) %>%
                group_by(HomeTeam) %>% 
                summarise_at(vars(value),list(HomeOffs = sum))%>% 
                setNames(c("Team","HomeOffs"))


AwayOff <- data %>%
                group_by(AwayTeam) %>%
                summarise(AwayTeam,AF) %>%
                pivot_longer(cols = AF) %>%
                group_by(AwayTeam) %>% 
                summarise_at(vars(value),list(AwayOffs = sum)) %>% 
                setNames(c("Team","AwayOffs"))

TotalOff <- merge(HomeOff,AwayOff, by = "Team")

TotalOff %>%
  mutate(TotalOffs = rowSums(select_(.,"HomeOffs","AwayOffs"))) %>%
  arrange(desc(TotalOffs)) %>%
  head(5) %>%
  kable(digits = 2,"html",row.names = FALSE) %>%
  kable_styling(font_size = 20,bootstrap_options = c("striped","hover"))
```


## En cok korner kullanan 5 takim {.tabset}

### Table

```{r echo=FALSE, message=FALSE, warning=FALSE}
HomeCor <- data %>%
                group_by(HomeTeam) %>%
                summarise(HomeTeam,HC) %>%
                pivot_longer(cols = HC) %>%
                group_by(HomeTeam) %>% 
                summarise_at(vars(value),list(HomeCors = sum)) %>% 
                setNames(c("Team","HomeCors"))


AwayCor <- data %>%
                group_by(AwayTeam) %>%
                summarise(AwayTeam,AC) %>%
                pivot_longer(cols = AC) %>%
                group_by(AwayTeam) %>% 
                summarise_at(vars(value),list(AwayCors = sum)) %>% 
                setNames(c("Team","AwayCors"))

TotalCor <- merge(HomeCor,AwayCor, by = "Team")

TotalCor %>%
  mutate(TotalCors = rowSums(select_(.,"HomeCors","AwayCors"))) %>%
  arrange(desc(TotalCors)) %>%
  head(5) %>%
  kable(digits = 2,"html",row.names = FALSE) %>%
  kable_styling(font_size = 20,bootstrap_options = c("striped","hover"))
```

### Code

```{r message=FALSE, warning=FALSE}
HomeCor <- data %>%
                group_by(HomeTeam) %>%
                summarise(HomeTeam,HC) %>%
                pivot_longer(cols = HC) %>%
                group_by(HomeTeam) %>% 
                summarise_at(vars(value),list(HomeCors = sum)) %>% 
                setNames(c("Team","HomeCors"))


AwayCor <- data %>%
                group_by(AwayTeam) %>%
                summarise(AwayTeam,AC) %>%
                pivot_longer(cols = AC) %>%
                group_by(AwayTeam) %>% 
                summarise_at(vars(value),list(AwayCors = sum)) %>% 
                setNames(c("Team","AwayCors"))

TotalCor <- merge(HomeCor,AwayCor, by = "Team")

TotalCor %>%
  mutate(TotalCors = rowSums(select_(.,"HomeCors","AwayCors"))) %>%
  arrange(desc(TotalCors)) %>%
  head(5) %>%
  kable(digits = 2,"html",row.names = FALSE) %>%
  kable_styling(font_size = 20,bootstrap_options = c("striped","hover"))
```

## Evinde en cok gol yiyen 5 takim {.tabset}

### Table

```{r echo=FALSE, message=FALSE, warning=FALSE}
data %>%
  pivot_longer(cols = FTAG) %>%
  group_by(HomeTeam) %>% 
  summarise_at(vars(value),list(AwayTeamGoal = sum)) %>%
  arrange(desc(AwayTeamGoal)) %>%
  head(5) %>%
  kable("html",row.names = FALSE) %>%
  kable_styling(font_size = 20,bootstrap_options = c("striped","hover"))
```

### Code

```{r message=FALSE, warning=FALSE}
data %>%
  pivot_longer(cols = FTAG) %>%
  group_by(HomeTeam) %>% 
  summarise_at(vars(value),list(AwayTeamGoal = sum)) %>%
  arrange(desc(AwayTeamGoal)) %>%
  head(5) %>%
  kable("html",row.names = FALSE) %>%
  kable_styling(font_size = 20,bootstrap_options = c("striped","hover"))
```

## Evinde ilk yarida en cok gol yiyen 5 takim {.tabset}

### Table

```{r echo=FALSE, message=FALSE, warning=FALSE}
data %>%
  pivot_longer(cols = HTAG) %>%
  group_by(HomeTeam) %>%
  summarise_at(vars(value),list(AwayTeamGoal = sum)) %>%
  arrange(desc(AwayTeamGoal)) %>%
  head(5) %>%
  kable("html",row.names = FALSE) %>%
  kable_styling(font_size = 20,bootstrap_options = c("striped","hover"))
```

### Code

```{r message=FALSE, warning=FALSE}
data %>%
  pivot_longer(cols = HTAG) %>%
  group_by(HomeTeam) %>%
  summarise_at(vars(value),list(AwayTeamGoal = sum)) %>%
  arrange(desc(AwayTeamGoal)) %>%
  head(5) %>%
  kable("html",row.names = FALSE) %>%
  kable_styling(font_size = 20,bootstrap_options = c("striped","hover"))
```

## Evinde en cok gol atan 5 takim {.tabset}

### Table

```{r echo=FALSE, message=FALSE, warning=FALSE}
data %>%
  pivot_longer(cols = FTHG) %>%
  group_by(HomeTeam) %>%
  summarise_at(vars(value),list(HomeTeamGoal = sum)) %>%
  arrange(desc(HomeTeamGoal)) %>%
  head(5) %>%
  kable("html",row.names = FALSE) %>%
  kable_styling(font_size = 20,bootstrap_options = c("striped","hover"))
```

### Code

```{r message=FALSE, warning=FALSE}
data %>%
  pivot_longer(cols = FTHG) %>%
  group_by(HomeTeam) %>%
  summarise_at(vars(value),list(HomeTeamGoal = sum)) %>%
  arrange(desc(HomeTeamGoal)) %>%
  head(5) %>%
  kable("html",row.names = FALSE) %>%
  kable_styling(font_size = 20,bootstrap_options = c("striped","hover"))
```

## Evinde ilk yarida en cok gol atan 5 takim {.tabset}

### Table

```{r echo=FALSE, message=FALSE, warning=FALSE}
data %>%
  pivot_longer(cols = HTHG) %>%
  group_by(HomeTeam) %>%
  summarise_at(vars(value),list(HomeTeamGoal = sum)) %>%
  arrange(desc(HomeTeamGoal)) %>%
  head(5) %>%
  kable("html",row.names = FALSE) %>%
  kable_styling(font_size = 20,bootstrap_options = c("striped","hover"))
```

### Code

```{r message=FALSE, warning=FALSE}
data %>%
  pivot_longer(cols = HTHG) %>%
  group_by(HomeTeam) %>%
  summarise_at(vars(value),list(HomeTeamGoal = sum)) %>%
  arrange(desc(HomeTeamGoal)) %>%
  head(5) %>%
  kable("html",row.names = FALSE) %>%
  kable_styling(font_size = 20,bootstrap_options = c("striped","hover"))
```

## Deplasmanda en cok gol yiyen 5 takim {.tabset}

### Table

```{r echo=FALSE, message=FALSE, warning=FALSE}
data %>%
  pivot_longer(cols = FTHG) %>%
  group_by(AwayTeam) %>%
  summarise_at(vars(value),list(HomeTeamGoal = sum)) %>%
  arrange(desc(HomeTeamGoal)) %>%
  head(5) %>%
  kable("html",row.names = FALSE) %>%
  kable_styling(font_size = 20,bootstrap_options = c("striped","hover"))
```

### Code

```{r message=FALSE, warning=FALSE}
data %>%
  pivot_longer(cols = FTHG) %>%
  group_by(AwayTeam) %>%
  summarise_at(vars(value),list(HomeTeamGoal = sum)) %>%
  arrange(desc(HomeTeamGoal)) %>%
  head(5) %>%
  kable("html",row.names = FALSE) %>%
  kable_styling(font_size = 20,bootstrap_options = c("striped","hover"))
```

## Deplasmanda ilk yarida en cok gol yiyen 5 takim {.tabset}

### Table

```{r echo=FALSE, message=FALSE, warning=FALSE}
data %>%
  pivot_longer(cols = HTHG) %>%
  group_by(AwayTeam) %>%
  summarise_at(vars(value),list(HomeTeamGoal = sum)) %>%
  arrange(desc(HomeTeamGoal)) %>%
  head(5) %>%
  kable("html",row.names = FALSE) %>%
  kable_styling(font_size = 20,bootstrap_options = c("striped","hover"))
```

### Code

```{r message=FALSE, warning=FALSE}
data %>%
  pivot_longer(cols = HTHG) %>%
  group_by(AwayTeam) %>%
  summarise_at(vars(value),list(HomeTeamGoal = sum)) %>%
  arrange(desc(HomeTeamGoal)) %>%
  head(5) %>%
  kable("html",row.names = FALSE) %>%
  kable_styling(font_size = 20,bootstrap_options = c("striped","hover"))
```

## Deplasmanda en cok gol atan 5 takim {.tabset}

### Table

```{r echo=FALSE, message=FALSE, warning=FALSE}
data %>%
  pivot_longer(cols = FTAG) %>%
  group_by(AwayTeam) %>%
  summarise_at(vars(value),list(AwayTeamGoal = sum)) %>%
  arrange(desc(AwayTeamGoal)) %>%
  head(5) %>%
  kable("html",row.names = FALSE) %>%
  kable_styling(font_size = 20,bootstrap_options = c("striped","hover"))
```

### Code

```{r message=FALSE, warning=FALSE}
data %>%
  pivot_longer(cols = FTAG) %>%
  group_by(AwayTeam) %>%
  summarise_at(vars(value),list(AwayTeamGoal = sum)) %>%
  arrange(desc(AwayTeamGoal)) %>%
  head(5) %>%
  kable("html",row.names = FALSE) %>%
  kable_styling(font_size = 20,bootstrap_options = c("striped","hover"))
```

## Deplasmanda ilk yarida en cok gol atan 5 takim {.tabset}

### Table

```{r echo=FALSE, message=FALSE, warning=FALSE}
data %>%
  pivot_longer(cols = HTAG) %>%
  group_by(AwayTeam) %>%
  summarise_at(vars(value),list(AwayTeamGoal = sum)) %>%
  arrange(desc(AwayTeamGoal)) %>%
  head(5) %>%
  kable("html",row.names = FALSE) %>%
  kable_styling(font_size = 20,bootstrap_options = c("striped","hover"))
```

### Code

```{r message=FALSE, warning=FALSE}
data %>%
  pivot_longer(cols = HTAG) %>%
  group_by(AwayTeam) %>%
  summarise_at(vars(value),list(AwayTeamGoal = sum)) %>%
  arrange(desc(AwayTeamGoal)) %>%
  head(5) %>%
  kable("html",row.names = FALSE) %>%
  kable_styling(font_size = 20,bootstrap_options = c("striped","hover"))
```


```{r Model}

data$Date <- lubridate::mdy(data$Date)
data$Time <- hms::as_hms(data$Time)
data$FTR <- as.factor(data$FTR)
data$HTR <- as.factor(data$HTR)

data <- data %>% mutate(FTR= relevel(FTR,ref='H'),
                        HTR=relevel(HTR,ref='H'))

index<- createDataPartition(data$FTR,p=.70,list = FALSE)

train <- data[index,]
test<- data[-index,]




multinom_mod<- multinom(FTR ~ . ,data=train[c("FTR","HTR","FTHG","FTAG","HTHG","HTAG","HS","AS","HST","AST","HF","AF","HC","AC","HY","AY","HR","AR")])



```

```{r}


HomeBet <-data %>%  filter(FTR == "H") %>% 
  select("Date","HomeTeam","AwayTeam","FTR","B365H","BWH","IWH","PSH","WHH","VCH")


HomeBet$Max <- pmax(HomeBet$B365H,HomeBet$IWH,HomeBet$PSH,HomeBet$WHH,HomeBet$VCH)

AwayBet <-data %>%  filter(FTR == "A") %>% 
  select("Date","HomeTeam","AwayTeam","FTR","B365A","BWA","IWA","PSA","WHA","VCA")

AwayBet$Max <- pmax(AwayBet$B365A,AwayBet$IWA,AwayBet$PSA,AwayBet$WHA,AwayBet$VCA)
AwayBet

```

