---
title: "Reproducible Research Final Project"
author: "Erim Celen, Ozgur Polat, Bugra Duman"
date: "5/7/2021"
output: 
  html_document:
    theme: united
    highlight: tango
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include=FALSE}
library(readr)
library(tidyverse)
library(plyr)
library(dplyr)
library(kableExtra)
library(caret)
library(nnet)
library(gridExtra)
library(grid)
library(janitor)
```

## Data Source

**Source:**https://www.football-data.co.uk/data.php

Fulltime and halftime results for up to 22 European league divisions from 25 seasons back to 1993/94. Additional match statistics since 2000/01, including shots on goal, corners, fouls, offsides, bookings, red cards and referees, are also available for the major European football leagues, including the English Premiership and lower divisions, the Socttish Premiersip, German Budnesliga, Spanish la Liga, Italian Serie A and French Championnat.

Historical match betting odds data from up to 10 major online bookmakers are available back to 2000/01. Since 2005/06 average and maximum prices for match betting, total goals and Asian handicap have also been collected from Betbrain. Since 2017/2018, match statistics are available for all 22 divisions.

In this reproducible project you can simply use other datasets in this data source as well. For more information on the dataset please consult the data dictionary below.

## Data Description
All data is in csv format, ready for use within standard spreadsheet applications. Please note that some abbreviations are no longer in use (in particular odds from specific bookmakers no longer used) and refer to data collected in earlier seasons. For a current list of what bookmakers are included in the dataset please visit the link given above.

### Key to results data:
**Div =** League Division <br />
**Date =** Match Date (dd/mm/yy) <br />
**Time =** Time of match kick off <br />
**HomeTeam =** Home Team <br />
**AwayTeam =** Away Team <br />
**FTHG and HG =** Full Time Home Team Goals <br />
**FTAG and AG =** Full Time Away Team Goals <br />
**FTR and Res =** Full Time Result (H=Home Win, D=Draw, A=Away Win) <br />
**HTHG =** Half Time Home Team Goals <br />
**HTAG =** Half Time Away Team Goals <br />
**HTR =** Half Time Result (H=Home Win, D=Draw, A=Away Win) <br />

### Match Statistics (where available):
Attendance = Crowd Attendance <br />
Referee = Match Referee <br />
HS = Home Team Shots <br />
AS = Away Team Shots <br />
HST = Home Team Shots on Target <br />
AST = Away Team Shots on Target <br />
HHW = Home Team Hit Woodwork <br />
AHW = Away Team Hit Woodwork <br />
HC = Home Team Corners <br />
AC = Away Team Corners <br />
HF = Home Team Fouls Committed <br />
AF = Away Team Fouls Committed <br />
HFKC = Home Team Free Kicks Conceded <br />
AFKC = Away Team Free Kicks Conceded <br />
HO = Home Team Offsides <br />
AO = Away Team Offsides <br />
HY = Home Team Yellow Cards <br />
AY = Away Team Yellow Cards <br />
HR = Home Team Red Cards <br />
AR = Away Team Red Cards <br />

### Key to 1X2 (match) betting odds data:

B365H = Bet365 home win odds  <br />
B365D = Bet365 draw odds <br />
B365A = Bet365 away win odds <br />
BSH = Blue Square home win odds <br />
BSD = Blue Square draw odds <br />
BSA = Blue Square away win odds <br />
BWH = Bet&Win home win odds <br />
BWD = Bet&Win draw odds <br />
BWA = Bet&Win away win odds <br />
GBH = Gamebookers home win odds <br />
GBD = Gamebookers draw odds <br />
GBA = Gamebookers away win odds <br />
IWH = Interwetten home win odds <br />
IWD = Interwetten draw odds <br />
IWA = Interwetten away win odds <br />
LBH = Ladbrokes home win odds <br />
LBD = Ladbrokes draw odds <br />
LBA = Ladbrokes away win odds <br />
PSH and PH = Pinnacle home win odds <br />
PSD and PD = Pinnacle draw odds <br />
PSA and PA = Pinnacle away win odds <br />
SOH = Sporting Odds home win odds <br />
SOD = Sporting Odds draw odds <br />
SOA = Sporting Odds away win odds <br />
SBH = Sportingbet home win odds <br />
SBD = Sportingbet draw odds <br />
SBA = Sportingbet away win odds <br />
SJH = Stan James home win odds <br />
SJD = Stan James draw odds <br />
SJA = Stan James away win odds <br />
SYH = Stanleybet home win odds <br />
SYD = Stanleybet draw odds <br />
SYA = Stanleybet away win odds <br />
VCH = VC Bet home win odds <br />
VCD = VC Bet draw odds <br />
VCA = VC Bet away win odds <br />

Data import and imputation of the unused part. Imputated part is also not included in the data description. For full description please refer to: https://www.football-data.co.uk/notes.txt

```{r echo=FALSE, message=FALSE, warning=FALSE}
data <- read_csv(url("https://www.football-data.co.uk/mmz4281/1920/E0.csv"))
data <- data[1:41]
data %>% 
  head(10) %>% 
  kable("html",row.names = FALSE) %>%
  kable_styling(font_size = 20,bootstrap_options = c("striped","hover")) %>% 
  kableExtra::scroll_box(width = "100%")
  
```

## Data Analysis

## Teams in the league
Unique values in the HomeTeam gathered to be used as teams among the league as a new data frame.
```{r fig.align="center", echo=FALSE, message=TRUE, warning=FALSE}
Teams <- 
  data %>%
  select(HomeTeam) %>%
  unique() %>%
  arrange(HomeTeam) %>% 
  setNames(c("value"))


kable(col.names = NULL,list(Teams[1:10,],Teams[11:nrow(Teams),])) %>%
kable_styling(font_size = 20,position = "center")

```


## Standings Table
Since we do not have score table in the data we generate it.

```{r include=FALSE}
# Below we gather the winning team code and the type of the current team (home or away) we give scores to the teams who won the match (3 points) and draw (1 points)
points_table <-
  data %>%
  summarize(HomeTeam,AwayTeam,FTR) %>%
  mutate(class1 = ifelse(FTR == "D",1,3)) %>%
  pivot_longer(cols = c("HomeTeam","AwayTeam"))

points_table$class2 <- ifelse(substr(points_table$name, 1,1) == substr(points_table$FTR, 1,1),3,0)

# Here we sum all points for each teams (group by teams)
points_table <- 
  points_table %>%
  filter(class1 == 1 | class2 == 3) %>%
  mutate(final = ifelse(class1 != class2, class1, class2)) %>% 
  group_by(value) %>%
  summarise_at(vars(final),
               list(P=sum))

# Here we create a table that counts how many matches they won
wins_table <- 
  data %>%
  summarize(HomeTeam,AwayTeam,FTR) %>%
  filter(FTR != "D") %>%
  pivot_longer(cols = c("HomeTeam","AwayTeam"))

wins_table$w <- substr(wins_table$name, 1,1) == substr(wins_table$FTR, 1,1)  

wins_table <- 
  wins_table %>%
  filter(w == TRUE) %>%
  group_by(value) %>%
  summarise_at(vars(w),
               list(W=sum))
# Here we create a table that counts ghow many matches they lost
lost_table <-
  data %>%
  summarize(HomeTeam,AwayTeam,FTR) %>%
  filter(FTR != "D") %>%
  pivot_longer(cols = c("HomeTeam","AwayTeam"))

lost_table$l <- substr(lost_table$name, 1,1) != substr(lost_table$FTR, 1,1)

lost_table <- 
  lost_table %>%
  filter(l == TRUE) %>%
  group_by(value) %>%
  summarise_at(vars(l),
               list(L=sum))
# Here we create a table that counts ghow many matches they draw
draw_table <- 
  data %>%
  summarize(HomeTeam,AwayTeam,FTR) %>%
  filter(FTR == "D") %>%
  pivot_longer(cols = c("HomeTeam","AwayTeam")) %>%
  mutate(d = ifelse(FTR == "D",1,0)) %>% 
  group_by(value) %>% 
  summarise_at(vars(d),
               list(D=sum))

# Table for each team scored a goal at home
gfh_table <-
  data %>% 
  group_by(HomeTeam) %>%
  summarise_at(vars(FTHG),
               list(GFH=sum)) %>% 
  setNames(c("value","GFH"))

# Table for each team scored a goal at away
gfa_table <-
  data %>% 
  group_by(AwayTeam) %>%
  summarise_at(vars(FTAG),
               list(GFA=sum)) %>% 
  setNames(c("value","GFA"))

# Aggregation of previous two tables so it means total scored goals for each team
gf_table <- 
  ddply(merge(gfa_table, gfh_table, by = "value"),.(value),summarise, GF=sum(GFH+GFA))

# Table for each team conceded a goal at home
gah_table <-
  data %>% 
  group_by(HomeTeam) %>%
  summarise_at(vars(FTAG),
               list(GAH=sum)) %>% 
  setNames(c("value","GAH"))

# Table for each team conceded a goal at away
gaa_table <-
  data %>% 
  group_by(AwayTeam) %>%
  summarise_at(vars(FTHG),
               list(GAA=sum)) %>% 
  setNames(c("value","GAA"))

# Aggregation of previous two tables so it means total conceded goals for each team
ga_table <- 
  ddply(merge(gah_table, gaa_table, by = "value"),.(value),summarise, GA=sum(GAH+GAA))

# Differences between goals scored and goals conceded for each team
gd_table <-
  ddply(merge(ga_table, gf_table, by = "value"),.(value),summarise, GD=sum(GF-GA))

# Number of matches played at home for each team
hmp_table <-
  data %>% 
  get_dupes(HomeTeam) %>% 
  select(dupe_count,HomeTeam) %>% 
  unique() %>% 
  setNames(c("HMP","value"))

# Number of matches played at away for each team
amp_table <-
  data %>% 
  get_dupes(AwayTeam) %>% 
  select(dupe_count,AwayTeam) %>% 
  unique() %>% 
  setNames(c("AMP","value"))

# Aggregation of number of matches played at home and away for each team
mp_table <-
  ddply(merge(amp_table, hmp_table, by = "value"),.(value),summarise, MP=sum(HMP+AMP))

```



```{r echo=FALSE}
#All of the tables created below now aggregated in 'standindgs' data frame
standings <- cbind(Teams,mp_table,wins_table,draw_table,lost_table,gf_table,ga_table,gd_table,points_table)
standings <- standings[,c(-2,-4,-6,-8,-10,-12,-14,-16)]
colnames(standings)[1] <- "Teams"

standings <-
  standings %>% arrange(desc(P))

Rank <- 1:nrow(standings)
standings$Rank <- Rank

standings %>% 
  select(Rank,Teams,MP,W,D,L,GF,GA,GD,P) %>% 
  kable("html",row.names = FALSE) %>%
  kable_styling(font_size = 20,bootstrap_options = c("striped","hover")) 
```


## Number of Wins {.tabset}

### Table
Top 5 most winning teams
```{r echo=FALSE}
winners <- 
  data %>%
  summarize(HomeTeam,AwayTeam,FTR) %>%
  filter(FTR != "D") %>%
  pivot_longer(cols = c("HomeTeam","AwayTeam"))

winners$w <- substr(winners$name, 1,1) == substr(winners$FTR, 1,1)  
  
winners %>%
  filter(w == TRUE) %>%
  group_by(value) %>%
  summarise_at(vars(w),
               list(W=sum)) %>% 
  arrange(desc(W)) %>%
  head(5) %>%
  kable(col.names = c("Teams","Number of Wins"),digits = 2,"html",row.names = FALSE) %>%
  kable_styling(font_size = 20,bootstrap_options = c("striped","hover")) 
  
```

### Code

```{r}
winners <- 
  data %>%
  summarize(HomeTeam,AwayTeam,FTR) %>%
  filter(FTR != "D") %>%
  pivot_longer(cols = c("HomeTeam","AwayTeam"))

winners$w <- substr(winners$name, 1,1) == substr(winners$FTR, 1,1)  
  
winners %>%
  filter(w == TRUE) %>%
  group_by(value) %>%
  summarise_at(vars(w),
               list(W=sum)) %>% 
  arrange(desc(W)) %>%
  kable(col.names = c("Teams","Number of Wins"),digits = 2,"html",row.names = FALSE) %>%
  kable_styling(font_size = 20,bootstrap_options = c("striped","hover")) 
  
```



## Percentage of Shots on Target

```{r include=FALSE}
table <- 
  data %>% 
  summarise('Home Shot' = sum(HS), 
            'Home Shot on Target' = sum(HST), 
            'Away Shot' = sum(AS), 
            'Away Shot on Target' = sum(AST)) %>% 
  pivot_longer(everything())

table <- 
  table %>% 
  mutate(place = substr(name,1,4))

p1 <-  ggplot(table, aes(x=name, y=value, fill=place)) + 
            geom_bar(stat = "identity") +
            geom_text(aes(label = value)) +
            theme(axis.title.x = element_blank(),
                  axis.title.y = element_blank(),
                  axis.text.y = element_blank(),
                  axis.text.x = element_text(angle = 45,size = 8,hjust = 1),
                  axis.ticks.y = element_blank(),
                  legend.title = element_blank()) +
            scale_fill_manual(values = c("#d8b365", "#5ab4ac"))


proportions <- as.data.frame(c("Home","Away")) %>% setNames(c("name"))
proportions$value <- c(round(table[2,2] / table[1, 2],4) * 100,round(table[4,2] / table[3,2],4) * 100)
proportions$value = paste0('%', proportions$value)
```

```{r fig.align="center", echo=FALSE}
t1 <- tableGrob(proportions, theme = ttheme_minimal(), rows = NULL,cols = NULL)

grid.arrange(p1,t1, nrow=1)

```



## Most Played Game Hours {.tabset}

### Table

```{r echo=FALSE, message=FALSE, warning=FALSE}
data %>%
  group_by(Time) %>%
  tally(sort = T) %>%
  top_n(3) %>%
  kable(col.names = c("Time","Game Played"),digits = 2,"html",row.names = FALSE) %>%
  kable_styling(font_size = 20,bootstrap_options = c("striped","hover"))  
```

### Code

```{r message=FALSE, warning=FALSE}
data %>%
  group_by(Time) %>%
  tally(sort = T) %>%
  top_n(3) %>%
  kable(col.names = c("Time","Game Played"),digits = 2,"html",row.names = FALSE) %>%
  kable_styling(font_size = 20,bootstrap_options = c("striped","hover")) 
```


## Full Time Results {.tabset}

Home team always has the advantage since they have more fans in the stadium.

### Table

```{r echo=FALSE, message=FALSE, warning=FALSE}
data %>% 
  mutate(FTR = as_factor(FTR)) %>%
  mutate(FTR = recode_factor(FTR,A = "Away", H = "Home", D = "Draw")) %>%
  select(FTR) %>% 
  count() %>% 
  arrange(desc(freq)) %>%
  kable(col.names = c("Team","Wins"),"html",row.names = FALSE) %>%
  kable_styling(font_size = 20,bootstrap_options = c("striped","hover"))
```

### Table Code

```{r message=FALSE, warning=FALSE}
data %>% 
  mutate(FTR = as_factor(FTR)) %>%
  mutate(FTR = recode_factor(FTR,A = "Away", H = "Home", D = "Draw")) %>%
  select(FTR) %>% 
  count() %>% 
  arrange(desc(freq)) %>%
  kable(col.names = c("Team","Wins"),"html",row.names = FALSE) %>%
  kable_styling(font_size = 20,bootstrap_options = c("striped","hover"))
```

### Plot

```{r echo=FALSE, message=FALSE, warning=FALSE}
data %>% 
  mutate(FTR = as_factor(FTR)) %>%
  mutate(FTR = recode_factor(FTR,A = "Away", H = "Home", D = "Draw")) %>%
  select(FTR) %>%
  count() %>%
  ggplot(aes(x="", y=freq, fill=FTR)) +
  geom_bar(stat = "identity", width=1) +
  coord_polar(theta = "y", start = 0) +
  scale_fill_manual(values=c("#B81D13", "#008450","#EFB700")) +
  geom_text(aes(label = freq),position = position_stack(vjust = 0.5)) +
  theme_void() +
  labs(fill = NULL)

```

### Plot Code

```{r message=FALSE, warning=FALSE}
data %>% 
  mutate(FTR = as_factor(FTR)) %>%
  mutate(FTR = recode_factor(FTR,A = "Away", H = "Home", D = "Draw")) %>%
  select(FTR) %>%
  count() %>%
  ggplot(aes(x="", y=freq, fill=FTR)) +
  geom_bar(stat = "identity", width=1) +
  coord_polar(theta = "y", start = 0) +
  scale_fill_manual(values=c("#B81D13", "#008450","#EFB700")) +
  geom_text(aes(label = freq),position = position_stack(vjust = 0.5)) +
  theme_void() +
  labs(fill = NULL)

```

## Games with most goals {.tabset}

### Table

```{r echo=FALSE, message=FALSE, warning=FALSE}
data %>%
  select(Date,HomeTeam,AwayTeam,FTHG,FTAG) %>%
  mutate(TG = rowSums(select_(.,"FTHG","FTAG"))) %>% 
  arrange(desc(TG)) %>%
  head(3) %>%
  select(-TG)%>%
  kable(digits = 2,"html",row.names = FALSE) %>%
  kable_styling(font_size = 20,bootstrap_options = c("striped","hover"))
```

### Code

```{r message=FALSE, warning=FALSE}
data %>%
  select(Date,HomeTeam,AwayTeam,FTHG,FTAG) %>%
  mutate(TG = rowSums(select_(.,"FTHG","FTAG"))) %>% 
  arrange(desc(TG)) %>%
  head(3) %>%
  select(-TG)%>%
  kable(digits = 2,"html",row.names = FALSE) %>%
  kable_styling(font_size = 20,bootstrap_options = c("striped","hover"))
```

## Average Odds {.tabset}

### Table

```{r echo=FALSE, message=FALSE, warning=FALSE}
data %>%
  mutate(B365s = rowSums(.[grep("B365",names(.))]),
         BWs = rowSums(.[grep("BW",names(.))]),
         IWs = rowSums(.[grep("IW",names(.))]),
         PSs = rowSums(.[grep("PS",names(.))]),
         WHs = rowSums(.[grep("WH",names(.))]),
         VCs = rowSums(.[grep("VC",names(.))])) %>%
  summarise(Bet365 = mean(B365s),
            BetWin = mean(BWs),
            Interwetten = mean(IWs),
            Pinnacle = mean(PSs),
            WilliamHill = mean(WHs),
            VCBet = mean(VCs))%>%
  pivot_longer(everything()) %>%
  arrange(desc(value)) %>%
  kable(digits = 2,"html",row.names = FALSE, col.names = c("Bet Platform","Average of Total odds")) %>%
  kable_styling(font_size = 20,bootstrap_options = c("striped","hover"))
  
```

### Code

```{r message=FALSE, warning=FALSE}
data %>%
  mutate(B365s = rowSums(.[grep("B365",names(.))]),
         BWs = rowSums(.[grep("BW",names(.))]),
         IWs = rowSums(.[grep("IW",names(.))]),
         PSs = rowSums(.[grep("PS",names(.))]),
         WHs = rowSums(.[grep("WH",names(.))]),
         VCs = rowSums(.[grep("VC",names(.))])) %>%
  summarise(Bet365 = mean(B365s),
            BetWin = mean(BWs),
            Interwetten = mean(IWs),
            Pinnacle = mean(PSs),
            WilliamHill = mean(WHs),
            VCBet = mean(VCs))%>%
  pivot_longer(everything()) %>%
  arrange(desc(value)) %>%
  kable(digits = 2,"html",row.names = FALSE, col.names = c("Bet Platform","Average of Total odds")) %>%
  kable_styling(font_size = 20,bootstrap_options = c("striped","hover"))
  
```

## Mean of Cards {.tabset}

### Table

```{r echo=FALSE, message=FALSE, warning=FALSE}
data %>%
  mutate(YellowCards = rowSums(select_(.,"HY","AY")),
         RedCards = rowSums(select_(.,"HR","AR"))) %>%
  summarise(RedCard = mean(RedCards) ,
            YellowCard = mean(YellowCards )) %>%
  pivot_longer(everything()) %>%
  kable(digits = 2,"html", row.names = FALSE, col.names = c("Type of Card","Average of Card per game")) %>%
  kable_styling(font_size = 20,bootstrap_options = c("striped","hover")) %>%
  row_spec(1,background = "#FF0000",color = "black") %>%
  row_spec(2,background = "yellow",color = "black")
```

### Code

```{r message=FALSE, warning=FALSE}
data %>%
  mutate(YellowCards = rowSums(select_(.,"HY","AY")),
         RedCards = rowSums(select_(.,"HR","AR"))) %>%
  summarise(RedCard = mean(RedCards) ,
            YellowCard = mean(YellowCards )) %>%
  pivot_longer(everything()) %>%
  kable(digits = 2,"html", row.names = FALSE, col.names = c("Type of Card","Average of Card per game")) %>%
  kable_styling(font_size = 20,bootstrap_options = c("striped","hover")) %>%
  row_spec(1,background = "#FF0000",color = "black") %>%
  row_spec(2,background = "yellow",color = "black")
```

## Top 5 teams that shoot the ball most {.tabset}

### Table

```{r echo=FALSE, message=FALSE, warning=FALSE}
HomeShot <- data %>%
                pivot_longer(cols = HS) %>% 
                group_by(HomeTeam) %>% 
                summarise_at(vars(value),list(HomeShots=sum)) %>% 
                setNames(c("Team","HomeShots"))
                

AwayShot <- data %>%
                pivot_longer(cols = AS) %>%
                group_by(AwayTeam) %>% 
                summarise_at(vars(value),list(AwayShots = sum)) %>% 
                setNames(c("Team","AwayShots"))

TotalShot <- merge(HomeShot,AwayShot, by = "Team")

TotalShot %>%
  mutate(TotalShots = rowSums(select_(.,"HomeShots","AwayShots"))) %>%
  arrange(desc(TotalShots)) %>%
  head(5) %>%
  kable(digits = 2,"html",row.names = FALSE) %>%
  kable_styling(font_size = 20,bootstrap_options = c("striped","hover"))
```

### Code

```{r message=FALSE, warning=FALSE}
HomeShot <- data %>%
                pivot_longer(cols = HS) %>% 
                group_by(HomeTeam) %>% 
                summarise_at(vars(value),list(HomeShots=sum)) %>% 
                setNames(c("Team","HomeShots"))
                

AwayShot <- data %>%
                pivot_longer(cols = AS) %>%
                group_by(AwayTeam) %>% 
                summarise_at(vars(value),list(AwayShots = sum)) %>% 
                setNames(c("Team","AwayShots"))

TotalShot <- merge(HomeShot,AwayShot, by = "Team")

TotalShot %>%
  mutate(TotalShots = rowSums(select_(.,"HomeShots","AwayShots"))) %>%
  arrange(desc(TotalShots)) %>%
  head(5) %>%
  kable(digits = 2,"html",row.names = FALSE) %>%
  kable_styling(font_size = 20,bootstrap_options = c("striped","hover"))
```

## Top 5 teams that commited fouls {.tabset}

### Table

```{r echo=FALSE, message=FALSE, warning=FALSE}
HomeOff <- data %>%
                pivot_longer(cols = HF) %>%
                group_by(HomeTeam) %>% 
                summarise_at(vars(value),list(HomeOffs = sum))%>% 
                setNames(c("Team","HomeFouls"))


AwayOff <- data %>%
                pivot_longer(cols = AF) %>%
                group_by(AwayTeam) %>% 
                summarise_at(vars(value),list(AwayOffs = sum)) %>% 
                setNames(c("Team","AwayFouls"))

TotalOff <- merge(HomeOff,AwayOff, by = "Team")

TotalOff %>%
  mutate(TotalOffs = rowSums(select_(.,"HomeFouls","AwayFouls"))) %>%
  arrange(desc(TotalOffs)) %>%
  head(5) %>%
  kable(digits = 2,"html",row.names = FALSE) %>%
  kable_styling(font_size = 20,bootstrap_options = c("striped","hover"))
```

### Code

```{r message=FALSE, warning=FALSE}
HomeOff <- data %>%
                pivot_longer(cols = HF) %>%
                group_by(HomeTeam) %>% 
                summarise_at(vars(value),list(HomeOffs = sum))%>% 
                setNames(c("Team","HomeOffs"))


AwayOff <- data %>%
                pivot_longer(cols = AF) %>%
                group_by(AwayTeam) %>% 
                summarise_at(vars(value),list(AwayOffs = sum)) %>% 
                setNames(c("Team","AwayOffs"))

TotalOff <- merge(HomeOff,AwayOff, by = "Team")

TotalOff %>%
  mutate(TotalOffs = rowSums(select_(.,"HomeOffs","AwayOffs"))) %>%
  arrange(desc(TotalOffs)) %>%
  head(5) %>%
  kable(digits = 2,"html",row.names = FALSE) %>%
  kable_styling(font_size = 20,bootstrap_options = c("striped","hover"))
```


## Top 5 teams that awarded with corners {.tabset}

### Table

```{r echo=FALSE, message=FALSE, warning=FALSE}
HomeCor <- data %>%
                pivot_longer(cols = HC) %>%
                group_by(HomeTeam) %>% 
                summarise_at(vars(value),list(HomeCors = sum)) %>% 
                setNames(c("Team","HomeCors"))


AwayCor <- data %>%
                pivot_longer(cols = AC) %>%
                group_by(AwayTeam) %>% 
                summarise_at(vars(value),list(AwayCors = sum)) %>% 
                setNames(c("Team","AwayCors"))

TotalCor <- merge(HomeCor,AwayCor, by = "Team")

TotalCor %>%
  mutate(TotalCors = rowSums(select_(.,"HomeCors","AwayCors"))) %>%
  arrange(desc(TotalCors)) %>%
  head(5) %>%
  kable(digits = 2,"html",row.names = FALSE) %>%
  kable_styling(font_size = 20,bootstrap_options = c("striped","hover"))
```

### Code

```{r message=FALSE, warning=FALSE}
HomeCor <- data %>%
                pivot_longer(cols = HC) %>%
                group_by(HomeTeam) %>% 
                summarise_at(vars(value),list(HomeCors = sum)) %>% 
                setNames(c("Team","HomeCors"))


AwayCor <- data %>%
                pivot_longer(cols = AC) %>%
                group_by(AwayTeam) %>% 
                summarise_at(vars(value),list(AwayCors = sum)) %>% 
                setNames(c("Team","AwayCors"))

TotalCor <- merge(HomeCor,AwayCor, by = "Team")

TotalCor %>%
  mutate(TotalCors = rowSums(select_(.,"HomeCors","AwayCors"))) %>%
  arrange(desc(TotalCors)) %>%
  head(5) %>%
  kable(digits = 2,"html",row.names = FALSE) %>%
  kable_styling(font_size = 20,bootstrap_options = c("striped","hover"))
```

## Top 5 teams that conceded most goals at home {.tabset}

### Table

```{r echo=FALSE, message=FALSE, warning=FALSE}
data %>%
  pivot_longer(cols = FTAG) %>%
  group_by(HomeTeam) %>% 
  summarise_at(vars(value),list(AwayTeamGoal = sum)) %>%
  arrange(desc(AwayTeamGoal)) %>%
  head(5) %>%
  kable("html",row.names = FALSE) %>%
  kable_styling(font_size = 20,bootstrap_options = c("striped","hover"))
```

### Code

```{r message=FALSE, warning=FALSE}
data %>%
  pivot_longer(cols = FTAG) %>%
  group_by(HomeTeam) %>% 
  summarise_at(vars(value),list(AwayTeamGoal = sum)) %>%
  arrange(desc(AwayTeamGoal)) %>%
  head(5) %>%
  kable("html",row.names = FALSE) %>%
  kable_styling(font_size = 20,bootstrap_options = c("striped","hover"))
```

## Top 5 teams that conceded most goals at home in the first half {.tabset}

### Table

```{r echo=FALSE, message=FALSE, warning=FALSE}
data %>%
  pivot_longer(cols = HTAG) %>%
  group_by(HomeTeam) %>%
  summarise_at(vars(value),list(AwayTeamGoal = sum)) %>%
  arrange(desc(AwayTeamGoal)) %>%
  head(5) %>%
  kable("html",row.names = FALSE) %>%
  kable_styling(font_size = 20,bootstrap_options = c("striped","hover"))
```

### Code

```{r message=FALSE, warning=FALSE}
data %>%
  pivot_longer(cols = HTAG) %>%
  group_by(HomeTeam) %>%
  summarise_at(vars(value),list(AwayTeamGoal = sum)) %>%
  arrange(desc(AwayTeamGoal)) %>%
  head(5) %>%
  kable("html",row.names = FALSE) %>%
  kable_styling(font_size = 20,bootstrap_options = c("striped","hover"))
```

## Top 5 teams that scored most goals at home {.tabset}

### Table

```{r echo=FALSE, message=FALSE, warning=FALSE}
data %>%
  pivot_longer(cols = FTHG) %>%
  group_by(HomeTeam) %>%
  summarise_at(vars(value),list(HomeTeamGoal = sum)) %>%
  arrange(desc(HomeTeamGoal)) %>%
  head(5) %>%
  kable("html",row.names = FALSE) %>%
  kable_styling(font_size = 20,bootstrap_options = c("striped","hover"))
```

### Code

```{r message=FALSE, warning=FALSE}
data %>%
  pivot_longer(cols = FTHG) %>%
  group_by(HomeTeam) %>%
  summarise_at(vars(value),list(HomeTeamGoal = sum)) %>%
  arrange(desc(HomeTeamGoal)) %>%
  head(5) %>%
  kable("html",row.names = FALSE) %>%
  kable_styling(font_size = 20,bootstrap_options = c("striped","hover"))
```

## Top 5 teams that scored most goals at home in the first half {.tabset}

### Table

```{r echo=FALSE, message=FALSE, warning=FALSE}
data %>%
  pivot_longer(cols = HTHG) %>%
  group_by(HomeTeam) %>%
  summarise_at(vars(value),list(HomeTeamGoal = sum)) %>%
  arrange(desc(HomeTeamGoal)) %>%
  head(5) %>%
  kable("html",row.names = FALSE) %>%
  kable_styling(font_size = 20,bootstrap_options = c("striped","hover"))
```

### Code

```{r message=FALSE, warning=FALSE}
data %>%
  pivot_longer(cols = HTHG) %>%
  group_by(HomeTeam) %>%
  summarise_at(vars(value),list(HomeTeamGoal = sum)) %>%
  arrange(desc(HomeTeamGoal)) %>%
  head(5) %>%
  kable("html",row.names = FALSE) %>%
  kable_styling(font_size = 20,bootstrap_options = c("striped","hover"))
```

## Top 5 teams that conceded most goals at away {.tabset}

### Table

```{r echo=FALSE, message=FALSE, warning=FALSE}
data %>%
  pivot_longer(cols = FTHG) %>%
  group_by(AwayTeam) %>%
  summarise_at(vars(value),list(HomeTeamGoal = sum)) %>%
  arrange(desc(HomeTeamGoal)) %>%
  head(5) %>%
  kable("html",row.names = FALSE) %>%
  kable_styling(font_size = 20,bootstrap_options = c("striped","hover"))
```

### Code

```{r message=FALSE, warning=FALSE}
data %>%
  pivot_longer(cols = FTHG) %>%
  group_by(AwayTeam) %>%
  summarise_at(vars(value),list(HomeTeamGoal = sum)) %>%
  arrange(desc(HomeTeamGoal)) %>%
  head(5) %>%
  kable("html",row.names = FALSE) %>%
  kable_styling(font_size = 20,bootstrap_options = c("striped","hover"))
```

## Top 5 teams that conceded most goals at away in the first half {.tabset}

### Table

```{r echo=FALSE, message=FALSE, warning=FALSE}
data %>%
  pivot_longer(cols = HTHG) %>%
  group_by(AwayTeam) %>%
  summarise_at(vars(value),list(HomeTeamGoal = sum)) %>%
  arrange(desc(HomeTeamGoal)) %>%
  head(5) %>%
  kable("html",row.names = FALSE) %>%
  kable_styling(font_size = 20,bootstrap_options = c("striped","hover"))
```

### Code

```{r message=FALSE, warning=FALSE}
data %>%
  pivot_longer(cols = HTHG) %>%
  group_by(AwayTeam) %>%
  summarise_at(vars(value),list(HomeTeamGoal = sum)) %>%
  arrange(desc(HomeTeamGoal)) %>%
  head(5) %>%
  kable("html",row.names = FALSE) %>%
  kable_styling(font_size = 20,bootstrap_options = c("striped","hover"))
```

## Top 5 teams that scored most goals at away {.tabset}

### Table

```{r echo=FALSE, message=FALSE, warning=FALSE}
data %>%
  pivot_longer(cols = FTAG) %>%
  group_by(AwayTeam) %>%
  summarise_at(vars(value),list(AwayTeamGoal = sum)) %>%
  arrange(desc(AwayTeamGoal)) %>%
  head(5) %>%
  kable("html",row.names = FALSE) %>%
  kable_styling(font_size = 20,bootstrap_options = c("striped","hover"))
```

### Code

```{r message=FALSE, warning=FALSE}
data %>%
  pivot_longer(cols = FTAG) %>%
  group_by(AwayTeam) %>%
  summarise_at(vars(value),list(AwayTeamGoal = sum)) %>%
  arrange(desc(AwayTeamGoal)) %>%
  head(5) %>%
  kable("html",row.names = FALSE) %>%
  kable_styling(font_size = 20,bootstrap_options = c("striped","hover"))
```

## Top 5 teams that scored most goals at away in the first half {.tabset}

### Table

```{r echo=FALSE, message=FALSE, warning=FALSE}
data %>%
  pivot_longer(cols = HTAG) %>%
  group_by(AwayTeam) %>%
  summarise_at(vars(value),list(AwayTeamGoal = sum)) %>%
  arrange(desc(AwayTeamGoal)) %>%
  head(5) %>%
  kable("html",row.names = FALSE) %>%
  kable_styling(font_size = 20,bootstrap_options = c("striped","hover"))
```

### Code

```{r message=FALSE, warning=FALSE}
data %>%
  pivot_longer(cols = HTAG) %>%
  group_by(AwayTeam) %>%
  summarise_at(vars(value),list(AwayTeamGoal = sum)) %>%
  arrange(desc(AwayTeamGoal)) %>%
  head(5) %>%
  kable("html",row.names = FALSE) %>%
  kable_styling(font_size = 20,bootstrap_options = c("striped","hover"))
```


